Optimal strategies in mental rotation tasks

### 2013-05-13 man/final-project.tex
Move rotations figure, and add results for BQ model

The rotations computed by the nonparametric model are strongly
correlated with the true rotations ($\rho=0.73$). In general, the
nonparametric model rotates much more than should be necessary; this
is because the Bayesian quadrature estimate of $Z$ is too large to
accept either hypothesis until a significant portion of the rotations
have been sampled.

>>>>

The rotations computed by the nonparametric model were strongly
correlated with the true rotations ($\rho=0.73$, see Figure
\ref{fig:rotations}, right panel). This is because the nonparametric
model does not get stuck as easily on local optima: it will continue
rotating until it is confident that its estimate of $Z$ is accurate.

Correspondingly, the nonparametric model is much more accurate in
choosing the correct hypothesis ($\ME{}=0.06$). As with the \naive{}
and parametric models, it mostly errs on $h_1$ stimuli
($\ME{}=0.1$). This appears to mostly be the result of choosing the
incorrect initial direction of rotation.

Similarly, because the nonparametric model actively attemps to obtain
an accurate estimate of $Z$, its estimate of $Z$ is indeed fairly
accurate ($\MSE{}=0.10$). This is slightly higher than the
nonparametric model, but is due to a few outliers. If we again exclude
stimuli for which $Z$ is greatly overestimated ($Z\geq 0.3$), the
nonparametric model's error decreases significantly ($\MSE{}=0.03$).
